%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBold}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListHeading}[1]{\textbf{#1}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://anumittal.in/}{\Large Anu Mittal}} & Email : \href{mailto:anu22mittal@gmail.com}{anu22mittal@gmail.com}\\
  \href{http://anumittal.in/}{http://anumittal.in/} & Mobile : +91-9971193839 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
  \resumeSubheading
      {Zomato}{Delhi, India}
      {iOS Engineer}{April 2017 - Present}
      \resumeItemListStart
       \resumeItemNoBold{Added support for RTL languages and responsive design for various device sizes using Auto Layout.}
       \resumeItemNoBold{Built the entire Table Reservation module of Zomato app and worked closely with the backend team to streamline the APIs.}
       \resumeItemNoBold{Made the zomato consumer app offline-first using Core Data to cache restaurant pages.}
       \resumeItemNoBold{Took initiative in setting up a simpler Git work flow to increase the team’s productivity.}
       \resumeItemNoBold{Added user activity tracking throughout the app to analyze user behaviour.}
       \resumeItemNoBold{Standardized internationalization of 6 languages and wrote script to automatically remove unused keys.}
       \resumeItemNoBold{Involved in resolving crashes on Zomato consumer app, helped raise app from 98.2\% to 99.33\% crash free.}
       \resumeItemNoBold{Part of 10+ releases, added features like hygiene rating, multiple user review, Gold UI update.}

      \resumeItemListEnd

    \resumeSubheading
      {Zomato}{Delhi, India}
      {Software Engineer}{Oct 2016 - April 2017}
      \resumeItemListStart
        \resumeItem{Moderation Dashboard}
          { Developed a ticket based moderation assignment system, used for moderating content for zomato sub-domains. Built a comment system and a photo viewer for menus. It replaced the third party ticket management system, HelpScout.}
        \begin{itemize}
            \item Designed a \textbf{normalized data model} to incorporate unstructured data collected from various sources
            \item Integrated an email service in ZFB to notify the merchant about the content updates of their listing.
        \end{itemize}

        \resumeItem{ZLog}
        {Developed ZLog (records moderators contributions) which includes generation of performance reports. The data was also used to get detailed weekly and monthly reports for moderators to perform data analytics.}
        \resumeItem{Content Health Monitoring System}
        {The system tracks the restaurant content validity and generates alerts for stale and invalid data.}
      \resumeItemListEnd

    \resumeSubheading
      {Google Summer of Code 2016}{Remote}
      {GSoC Developer, KDE}{April 2016 - August 2016}
      \resumeItemListStart
        \resumeItem{LabPlot}
          {Working on adding new plot types in LabPlot (a scientific data plotter application), namely histogram for continuous (quantitative) data and bar chart/plot for categorical data}
      \resumeItemListEnd
    \resumeSubheading
        {KDE}{Remote}
        {SoC Developer, KDE}{Dec 2014 - March 2015}
        \resumeItemListStart
          \resumeItem{Kalzium}
          {Ported project Kalzium under KDE Edu (based on C++ and Qt) to Qt5 using KDE framework 5 and Kubuntu OS.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages}
       {Objective-C, PHP, JavaScript, Java, Python, C++, C, SQL, Qt, HTML, CSS.}
    \resumeSubItem{Tools and Frameworks}
       {Git, Android, MySQL, jQuery, Qt Creator, Kdevelop, XCode, KDE Framework 5.}
 \resumeSubHeadingListEnd
%-------------------------------------------

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {BPIT, GGSIPU}{Delhi, India}
      {Bachelor of Engineering in Computer Science; Agg:81.50\%}{Aug. 2012 -- July 2016}
  \resumeSubHeadingListEnd

%--------TALKS & CONFERENCES------------
\section{Talks and Conferences}
 \resumeSubHeadingListStart
    \resumeSubItem{LinuxChix Meetup}
       {Talked about origin of Linux and KDE.}\hfill{India}
    \resumeSubItem{Akademy - Annual world summit of KDE}
       {Conducted a two hour workshop on Qt Quick 2.}\hfill{Spain}
    \resumeSubItem{FOSSASIA Summit 2017}
       {Gave a talk on ‘K’oding with KDE and presented LabPlot.}\hfill{Singapore}
    \resumeSubItem{KDE community, conf.kde.in 2016}
       {Presented KDE project in an international conference held in Jaipur.}\hfill{India}
 \resumeSubHeadingListEnd
%-------------------------------------------

%--------EXTRA CURRICULAR ACTIVITIES------------
% \section{Extra Curricular Activities}
%  \resumeSubHeadingListStart
%     \resumeSubItem{Core member, Literary Society(BPIT) (Unanimously elected from 300+ students)}
%       { Led a 3 tier team of 50 members to successfully organize the literary fest, Eloquence.}
%     \resumeSubItem{Event Head, Annual Cultural Fest-Corona, BPIT, 2014 (Spearheaded a team of 10 event coordinators)}
%       {Successfully managed the on-event activities and the entire logistics of 10+ events during Corona.}\hfill{Almeria, Spain}
%  \resumeSubHeadingListEnd
%-------------------------------------------

\end{document}